03 Data Vizualization

### 2022-04-06 03_data_viz.Rmd
add chromatogram and abund v turnover update

# BacDive Data
bacdive_FA <- readRDS(file = "cache/bacdive_FA")
bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")
```

@@

## dF

@@

@@

sample_files[10] %>% # choosing arbitrary file to plot
  iso_plot_continuous_flow_data(
# select data and aesthetics
data = c(2), color = id1, panel = id1,
# zoom in on time interval
time_interval = c(750, 4000),
# peak labels for all peaks > 2V
peak_bounds = TRUE,
peak_marker = FALSE,
peak_label = iso_format(rt),
#peak_label_size = 3,
peak_label_filter = analysis == 5685 & amp2 > 1
+ scale_color_npg() +
theme_classic() +
theme(strip.background = element_blank()))
```

>>>>

# BacDive Data
bacdive_FA <- readRDS(file = "cache/bacdive_FA")
bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")

# IRMS chromatogram data
sample_files <- readRDS(file = "cache/sample_files")
```

@@

## dF and turnover plot

@@

## Abundance versus turnover

```{r}
p_abundance_v_turnover <- turnover %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(
    x = compound_ug_per_g_soil,
    y = u_d,
    color = dF*10000
  )) +
  facet_wrap(vars(inc_time_d, soil), ncol = 3) +
  geom_point(alpha = 0.6) +
  scale_color_viridis_c() +
  theme_bw() +
  labs(x = "µg analyte per g soil",
       y = TeX("Turnover (d$^{-1}$)"),
       color = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  guides(color = guide_colorbar(barwidth = 0.5)) +
  theme(
    strip.background = element_blank(),
    panel.grid = element_blank(),
  )
p_abundance_v_turnover
```

@@

sample_files[10] %>% # choosing arbitrary file to plot
  iso_plot_continuous_flow_data(
    # select data and aesthetics
    data = c(2), color = id1, panel = id1,
    # zoom in on time interval
    time_interval = c(750, 4000),
    # peak labels for all peaks > 2V
    peak_bounds = TRUE,
    peak_marker = FALSE,
    #peak_label_size = 3
    ) +
    scale_color_npg() +
    theme_classic() +
    theme(strip.background = element_blank())
